better title eventually

### 2015-05-11 cs261n-paper/paper.tex
11-point font.
Per http://www.icir.org/vern/cs261n/writing.html.
Typo.
started using colors

%\documentclass{article}
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}

@@

what we want to contribute to the research community.

@@

We plant to solicit feedback on the design of this experiment at HotPETS2015.
Specifically, we would want a reliable way to target the testing of 
specific transports. But given that the average user would not have domain knowledge of 
what transports are for Tor, is there anything to infer from participants' selection of transports, 
or do we assume they are trying transports at random?

@@

\indent\indent This study will be conducted at the Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley. Recruitment will be conducted through Craigslist. 
Although Xlab provides a portal in which researchers can recruit a pre-registered user base,
we choose to not recruit through this portal, as their participants mostly consist of mostly Berkeley 
students. The laboratory setting consists of 36 Toshiba Tecra R850 laptops with cubicle walls 
separating each laptop. Since we do not have the ability to employ network-level firewalls in this
laboratory setting, we will use individual host firewalls to simulate the censorship environments.  
We will write and employ a browser extension will record user activity, such as how many times they 
clicked, what websites they were successfully able to visit, and how long they took to complete 
each task. This is because WHY? %ask david exactly why--technically. isn't the first hop in the clear?

@@

\section{Related Work} %%%
%%%Tor
The stopping points paper on Tor's usability ~\cite{norcie2012eliminating}. 
And that is pretty much it for Tor usability stuff. %find more if it exists

I guess that other literature on general usability applies here too. %so search for it. 
Especially look into browser configuration work. %do it to it.

%%%User behavior
\indent \indent Then also talk about any of the behaviors we are trying to mitigate,
or talk about the average user and what they know, how they are motivated,
just sketching out the environment in general.

%%% Other Usability stuff 
\indent \indent cite work which has made a huge impact on how people use it, and 
other things which still remain broken because of usability issues.

@@

GET THE LIST OF TASKS WE MADE THEM DO.

>>>>

%\documentclass{article}
\documentclass[letterpaper,twocolumn,11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}

@@

{\color {red} what we want to contribute to the research community.}

@@

We plan to solicit feedback on the design of this experiment at HotPETS2015.
Specifically, we would want a reliable way to target the testing of 
specific transports. But given that the average user would not have domain knowledge of 
what transports are for Tor, is there anything to infer from participants' selection of transports, 
or do we assume they are trying transports at random?

@@

\indent\indent This study will be conducted at the Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley. Recruitment will be conducted through Craigslist. 
Although Xlab provides a portal in which researchers can recruit a pre-registered user base,
we choose to not recruit through this portal, as their participants mostly consist of mostly Berkeley 
students. The laboratory setting consists of 36 Toshiba Tecra R850 laptops with cubicle walls 
separating each laptop. Since we do not have the ability to employ network-level firewalls in this
laboratory setting, we will use individual host firewalls to simulate the censorship environments.  
We will write and employ a browser extension will record user activity, such as how many times they 
clicked, what websites they were successfully able to visit, and how long they took to complete 
each task. {\color {red} This is because WHY?} %ask david exactly why--technically. isn't the first hop in the clear?

@@

\section{Related Work} %%%
%%%Tor
 {\color {red} The stopping points paper on Tor's usability ~\cite{norcie2012eliminating}. 
And that is pretty much it for Tor usability stuff.} %find more if it exists

{\color {red}  I guess that other literature on general usability applies here too. %so search for it. 
Especially look into browser configuration work. }

%%%User behavior
\indent \indent {\color {red}  Then also talk about any of the behaviors we are trying to mitigate,
or talk about the average user and what they know, how they are motivated,
just sketching out the environment in general.}

%%% Other Usability stuff 
\indent \indent {\color {red}  cite work which has made a huge impact on how people use it, and 
other things which still remain broken because of usability issues.}

@@

{\color {red}  GET THE LIST OF TASKS WE MADE THEM DO.}
